Blocking-resistant communication\\through domain fronting

### 2014-08-01 docs/meek.tex
Check some more off.

So far we do not find any obvious traffic characteristics that can be useful to reliably distinguish meek
from other HTTPS traffic.
The long-lived connections and few common packet sizes are
potential targets for a more concerted attack.
The fundamental problem we face is essentially that of steganography,
the need to make our traffic fit some model of ``normal'' traffic.
The problem is inherently difficult,
because it's difficult to say just what normal traffic \emph{is}.
It depends on the network environment;
it also depends on the endpoint.
Google is likely to be different than Akamai,
and it's hard to characterize what normal use of a CDN is:
they provide access to ordinary web sites,
but also video streams and software updates,
and not all clients are browsers.
The difficulty is symmetric;
if finding the right model is difficult task for us,
it is also difficult for the censor.
We have seen that censors prefer to use easy classifiers when they exist.
By removing the easy ways, we increase the cost to the censor.

>>>>

So far we do not find any obvious traffic characteristics that can be useful to reliably distinguish meek
from other HTTPS traffic.
The long-lived connections and few common packet sizes are
potential targets for a more concerted attack.
The fundamental problem we face is essentially that of steganography,
the need to make our traffic fit some model of ``normal'' traffic.
The problem is inherently difficult,
because it is difficult to say just what normal traffic \emph{is}.
It depends on the network environment;
it also depends on the endpoint.
Google is likely to be different than Akamai,
and it is hard to characterize what normal use of a CDN is:
they provide access to ordinary web sites,
but also video streams and software updates,
and not all clients are browsers.
The difficulty is symmetric;
if finding the right model is difficult task for us,
it is also difficult for the censor.
We have seen that censors prefer to use easy classifiers when they exist.
By removing the easy ways, we increase the cost to the censor.
